Distributional State Aggregation

### 2020-03-11 minutia/paper/paper.tex
Paper updated and new paper initiated
paper agg state clustering

    \begin{equation}
        \text { Bin width }=2 \frac{\operatorname{IQR}(x)}{\sqrt[3]{n}}
    \end{equation}

    where n is number of observations and $IQR(x)$ is the inter-quartile range of data.

@@

>>>>

    \begin{equation}
        |S_{agg}| = 2 \frac{\operatorname{IQR}(x)}{\sqrt[3]{n}}
    \end{equation}

    where n is number of observations and $IQR(x)$ is the inter-quartile range of data.f

    By having the inter-quartile range of data for each feature, a discretization policy can be calculated.

@@

    The original states with the closest \textit{calculated} values forgather to build aggregate states.
    For this purpose, state values are clustered by K-means analysis to calculate the relevant aggregate states.
